---
title: "p8105_hw5_yf2563"
author: "Yatong Feng"
date: "11/18/2020"
output: github_document
---

## Problem 0 - Setup
```{r setup, message = F}
library(tidyverse)
library(stringr)

knitr::opts_chunk$set(
  message = F,
  warning = F,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

#### 1.1.1 

Describe the raw data. 

```{r}
homicide_raw_df = 
  read_csv("data-homicides/homicide-data.csv")
```

**Brief Introduction:**

- The data included the location of the killing, whether an arrest was made and, in most cases, basic demographic information about each victim.
- The dimension of this resulting dataset is (`r dim(homicide_raw_df)`), which means that, there are `r dim(homicide_raw_df)[1]` observations and `r dim(homicide_raw_df)[2]` variables.
- The variables include `r ls(homicide_raw_df)`. 

**Create a city_state variable:**
```{r}
homicide_df = 
  homicide_raw_df %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


#### 1.1.2 

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides 

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

aggregate_df
```


#### 1.2

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```


#### 1.3 

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results_df
```


#### 1.4

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

longitudinal study: include a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

#### 2.1 

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

- dataframe: containing all file names (list.files function)
- Iterate over file names, read in data for each subject (purrr::map) and saving the result as a new variable in the dataframe

```{r}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    map_df(.x = path, read_csv)) %>% 
  bind_cols()

path_df
```

- Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary


```{r}
prob2_tidy_df = 
  path_df %>% 
  mutate(path = str_sub(path, 10, -5)) %>% 
  separate(path,
           into = c("control_arm", "subject_id"),
           sep = "_") %>% 
  mutate(control_arm = case_when(
    control_arm == "con" ~ "Control",
    control_arm == "exp" ~ "Experiment"
  )) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value")

prob2_tidy_df
```

- Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r}
prob2_tidy_df %>% 
  mutate(week = str_replace(week, "week_", "")) %>%
  ggplot(aes(x = week, y = value, group = subject_id, color = subject_id)) +
  geom_point() +
  geom_line() +
  facet_grid(~control_arm)
```
 
The control and experiment group have different trend. 
- For the control group: relatively stable around 1.25. 
- For the expose group: increasing trend over time. 



## Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30, sigma=5, mu=0. Generate 5000 datasets from the model


```{r}
set.seed(520)

sim_t_test = function(samp_size = 30, mu = 0, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(samp_size, mean = mu, sd = sigma),
  )
  
  sim_data  = t.test(sim_data) %>% 
  broom::tidy() %>% 
  mutate(mu = mu) %>% 
  select(mu, estimate, p.value)
  
  sim_data
  
  
}

# when mu = 0, generate 5000 results
sim_0 = map_dfr(0, ~rerun(5000, sim_t_test(mu = .x)))
sim_0
```


```{r}
# result for mu = {0,1,2,3,4,5,6}

output = map_dfr(0:6, ~rerun(5000, sim_t_test(mu = .x)))
output
```

#### Plot 1
- Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of mu on the x axis. Describe the association between effect size and power.

```{r}
plot1_df = 
output %>% 
    group_by(mu) %>% 
    filter(p.value < 0.05) %>% 
    summarize(proportion = n()/5000)
  
plot1_df %>% 
  ggplot(aes(x = mu, y = proportion))+
  geom_point()+
  geom_line() + 
  labs(
    title = "Association between effect size and power",
    x = "True mean",
    y = "The power of the test"
  )
```

**Comments:**

The plot have an obvious increasing trend. With the increase of the true mean, he proportion of times the null was rejected (the power of the test) also increase. The association between effect size and power is positive

#### Plot2

- Make a plot showing the average estimate of mu on the y axis and the true value of mu on the x axis. 
- Make a second plot (or overlay on the first) the average estimate of mu only in samples for which the null was rejected on the y axis and the true value of mu on the x axis. 


```{r}
average_estimate_rejected_df =
  output %>% 
  filter(p.value < 0.05) %>% 
  group_by(mu) %>% 
  summarise(average_estimate_rejected = mean(estimate))

average_estimate_df =
  output %>% 
  group_by(mu) %>% 
  summarise(average_estimate = mean(estimate)) %>% 
  mutate(average_estimate_rejected = pull(average_estimate_rejected_df, average_estimate_rejected)) %>% 
  pivot_longer(
    average_estimate:average_estimate_rejected,
    names_to = "type",
    values_to = "Average_estimate"
  )
  
```

```{r}
average_estimate_df %>% 
ggplot(aes(x = mu, y = Average_estimate, color = type)) +
  geom_point() +
  geom_line() + 
  labs(
    title = "Simulation difference among two groups",
    x = "True mean",
    y = "Average estimate of mu"
  )
```

- Is the sample average of mu across tests for which the null is rejected approximately equal to the true value of mu? Why or why not?

**Comments:**
- for mu = 0,  the sample average of mu across tests for which the null is rejected is relatively same as the true value of mu,  since the null hypothesis is mu = 0

- for mu > 0, the sample average of mu across tests for which the null is rejected is approximately equal to the true value of mu with the increase of the true mean. Since from from CLT and as the mu increase, the distribution of sample mean will follows a normal distribution with increasing mu and the rejection proportion of  will get bigger. 
